How did local health infrastructure and socio-political factors within different states and counties in the United States affect the disparities in COVID-19 outcomes, and what lessons can be learned for more targeted public health preparedness and response strategies in future pandemics?

### 2024-02-11 outputs/paper/paper.qmd
- updated replication and paper - deleted unecessary files - changed file names

# Save the plot to a file
ggsave("GHS_Index_Map.png", width = 11, height = 8)
```

@@

est_life
# Save the plot to a file
ggsave("Life_Exp.png", width = 10, height = 8)
```

@@

change_life_exp
ggsave("Change_Life_Exp.png", width = 10, height = 8)

@@

```
```{r}
#| echo: false
#| eval: true
#| warning: false

>>>>

@@

est_life

@@

change_life_exp

@@

```{r}
#| echo: false
#| eval: true
#| label: fig-Vote
#| fig-cap: Total Number of Votes by Top 10 Republican State
#| warning: false
